---
title: "supportR Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{supportR Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

```{r pre-setup, echo = FALSE, message = FALSE}
# devtools::install_github("njlyon/supportR")
# devtools::install_github("lter/lterpalettefinder")
```

## Overview

The `supportR` package is an amalgam of distinct functions I've written to accomplish small data wrangling, quality control, or visualization tasks. These functions tend to be short and narrowly-defined. An additional consequence of the motivation for creating them is that they tend to not be inter-related or united by a common theme. If this vignette feels somewhat scattered because of that, I hope it doesn't negatively affect how informative this is!

This vignette describes the main functions of `supportR` using the examples included in each function.

```{r setup}
# library(supportR)
```

### Summarizing Data



### Quality Control



### Data Visualization



### Reshaping Data



### Miscellaneous Other Functions



## Looking Ahead

If you have ideas for other functions that `lterpalettefinder` could contain, post them as [a GitHub Issue](https://github.com/lter/lterpalettefinder/issues) and we'll review them as soon as possible!
